\LARGE \bf A Pipeline for Assembling Collision and Near-Collision Dashcam Footage Datasets

### 2021-03-30 paper.tex
Added pr curve caption
sort class histogram by desc freq; grouped stationary/non-vehicular objects into "other"; various wording/grammar/conciseness improvements

%HAS BEEN REMOVED BECAUSE NOT FUNCTIONAL
%\subsection{Video Preprocessing}
%\subsection{Automatic Annotation}
%\subsection{Object Detection \& Tracking}
%\todo{Automated object detection not used right now?}
\subsection{Anonymization}
An important facet of automobile data aggregation is in eliminating biases and protecting the identities of depicted individuals. Consequently, our pipeline contains a post-processing stage in which we apply blurring masks to anonymize any personally identifiable information. Specifically, we provide the executor \texttt{FaceBlurrer}, which blurs faces. This executor first uses a MobileNet Single Shot MultiBox Detector \cite{yixuan_h_y_hu_2021_4642275} trained on the WIDERFACE dataset \cite{yang2016wider} to obtain the bounding boxes of all visibly identifiable individuals' faces at each frame of a given video and then applies a blurring mask over each bounding box. We have chosen to use a MobileNet SSD for this task because it achieves a good balance between accuracy and performance, while requiring relatively little memory \cite{yixuan_h_y_hu_2021_4642275}.

@@

\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.4\textwidth]{prcurve.png}
		\caption{\todo{Write caption, fix label (I don't think the term AUC is correct here since this value is actually the average precision from the training code)}}
		\label{fig:pr_curve}
\end{figure}

@@

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Objects by class},
      ylabel={Frequency (\# of objects)},
      xtick=data,
      xticklabels from table={\byclass}{X},
      xticklabel style={rotate=90}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byclass;
    \end{axis}
    \end{tikzpicture}
		\caption{Object by classes in our database}
		\label{fig:obj-by-class}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by participant},
      xlabel={Number of participants},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byactors}{X},
      xticklabel style={rotate=90}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byactors;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos by number of participants}
		\label{fig:vids-by-participant}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by agents},
      xlabel={Number of agents},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byagents}{X}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byagents;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos by number of agents}
		\label{fig:vids-by-agents}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by duration},
      xlabel={Duration (in frames)},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byduration}{X},
      xticklabel style={rotate=90}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byduration;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos by duration}
		\label{fig:vids-by-duration}
\end{figure}

@@

@@

There are many ways that we could improve our system, such as the following:
\begin{enumerate}
\item Labelling precision improvements: The current video-labelling process in the pipeline, manual bounding box drawing with linear interpolation between input frames, is prone to inserting mistaken bounding boxes that don't exactly match to the location of an object on certain frames. Automated labelling and custom interpolation would speed up the process of labelling and minimize the cases of misplaced bounding boxes. Labelling would be much faster if we had a (semi-)automated process of detecting objects and tracking them over frames. There are models for object detection that behave reasonably well which we could use, but they would still need to be augmented by a review process. For object tracking, there are simple heuristic algorithms that could be used. Being able to modify the method of interpolation between frames beyond the default linear interpolation would allow for more bounding box precision between large input frame windows. Moreover, given a type of interpolation is stored in the metadata, we probably shouldn't store all interpolated frames, rather than just the ones the user has entered. While linear interpolation works great for entering a frame every 10 frames, supporting more interpolations could be great for faster data entry, or even for supporting affine transformations on more complex bounds.

>>>>

%HAS BEEN REMOVED BECAUSE NOT FUNCTIONAL
%\subsection{Video Preprocessing}
%\subsection{Automatic Annotation}
%\subsection{Object Detection \& Tracking}
%\todo{Automated object detection not used right now?}
\subsection{Anonymization}
An important facet of automobile data aggregation is in eliminating biases and protecting the identities of depicted individuals. Consequently, our pipeline contains a post-processing stage in which we anonymize personally identifiable information. Specifically, we provide the executor \texttt{FaceBlurrer}, which blurs faces. This executor first uses a MobileNet Single Shot MultiBox Detector \cite{yixuan_h_y_hu_2021_4642275} trained on the WIDERFACE dataset \cite{yang2016wider} to obtain the bounding boxes of all visibly identifiable individuals' faces at each frame of a given video, and then applies a blurring mask over each bounding box. We have chosen to use a MobileNet SSD for this task because it achieves a good balance between accuracy and performance, while requiring relatively little memory \cite{yixuan_h_y_hu_2021_4642275}.

@@

\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.4\textwidth]{prcurve.png}
		\caption{Pre-trained DSARNN Precision-Recall curve on prototype dataset}
		\label{fig:pr_curve}
\end{figure}

@@

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Objects by class},
      ylabel={Frequency (\# of objects)},
      xtick=data,
      xticklabels from table={\byclass}{X},
      xticklabel style={rotate=90}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byclass;
    \end{axis}
    \end{tikzpicture}
		\caption{Objects grouped by class}
		\label{fig:obj-by-class}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by participant},
      xlabel={Number of participants},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byactors}{X},
      xticklabel style={rotate=90}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byactors;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos grouped by number of participants}
		\label{fig:vids-by-participant}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by agents},
      xlabel={Number of agents},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byagents}{X}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byagents;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos grouped by number of agents}
		\label{fig:vids-by-agents}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by duration},
      xlabel={Duration (in frames)},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byduration}{X},
      xticklabel style={rotate=90}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byduration;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos grouped by duration}
		\label{fig:vids-by-duration}
\end{figure}

@@

\todo{Explain the "other" category in the class histogram. These are stationary/non-vehicular objects.}
\todo{Add a paragraph explaining the key characteristics of Figures 5-10.}

@@

There are many ways that we could improve our system, such as the following:
\begin{enumerate}
\item Labelling precision improvements: The current video-labelling process in the pipeline, manual bounding box drawing with linear interpolation between input frames, is prone to inserting mistaken bounding boxes that don't exactly match to the location of an object on certain frames. Automated labelling and custom interpolation would speed up the process of labelling and minimize the cases of misplaced bounding boxes. Labelling would be much faster if we had a semi-automated process of detecting objects and tracking them over frames. There are models for object detection that behave reasonably well which we could use, but they would still need to be augmented by a review process. For object tracking, there are simple heuristic algorithms that could be used. Being able to modify the method of interpolation between frames beyond the default linear interpolation would allow for more bounding box precision between large input frame windows. Moreover, given a type of interpolation is stored in the metadata, we probably shouldn't store all interpolated frames, rather than just the ones the user has entered. While linear interpolation works great for entering a frame every 10 frames, supporting more interpolations could be great for faster data entry, or even for supporting affine transformations on more complex bounds.
